---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "vignettes",
  out.width = "100%"
)
library(BMIMIC)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# BMIMIC

## Overview

This package is for generating example simulation data for BMIMIC model which is introduced in **Bayesian MIMIC for DIF Detection under Violation of Equal Variance Assumption**. More information can be found in **Bayesian MIMIC for DIF Detection under Violation of Equal Variance Assumption**.

## Install

```{r}
devtools::install_github("sooyongl/BMIMIC")
```


## Generate Data

```{r}
library(BMIMIC)
library(rstan)

generated_data <-
  mkData(N1         = 500,
         N2         = 500,
         nitem      = 10,
         mu_2       = 0.2,
         var_2      = 2,
         uni_dif    = c(0,0,0,0,0.2,0.2,0.2,0,0,0),
         nonuni_dif = c(0,0,0,0,0,0,0,0.2,0.2,0.2),
         anchor_n   = 4)
```

## Generated data

### Item parameters
```{r}
generated_data$ipars
```

### Item response
```{r}
generated_data$response
```

### Group assignments
```{r}
generated_data$group
```

## Run BMIMIC model via rstan

### stan code

```{r eval = T, echo = F}
cat(
  paste(
    readLines(
      file.path(
        system.file("stan", package = "BMIMIC"),"BMIMIC_example.stan")
      ),
    collapse = "\n")
  )
```

### Run stan

```{r}
stan_fit <-
  rstan::stan(
    file = file.path(system.file("stan", package = "BMIMIC"),
                     "BMIMIC_example.stan"),
    data   = generated_data$stan_data
  )

summary(stan_fit)
```

